\section{Introduction}
We already know syntactic unification where we try to find a substitution $\sigma$ to make two terms syntactically equal. But what if we know something about the function symbols in our terms for example we know that $f$ is idempotent (i.e. $f(x,x)\approx x$). The syntactic unification problem $S:=\left\lbrace f(a,x)\stackrel{?}{=}x\right\rbrace$ where $a$ is a constant and $x$ a variable does not have a solution. This is where equational unification comes in handy because it considers equality modulo an equational theory $\approx_E$: given terms $s$ and $t$ is there a substitution $\sigma$ such that $\sigma(s)\approx_E \sigma(t)$. Let $I\models f(x,x)\approx x$ now the substitution $\sigma:=\left\lbrace x\mapsto a\right\rbrace $ is a solution of the $I$-unification problem $S:=\left\lbrace f(a,x)\approxq_I x\right\rbrace$ since $f(a,a)\approx_Ia$. 

Here we will only consider Boolean unification in more detail but there are also other interesting equational theories like $AC$, i.e. the theory that axiomatizes associativity and commutativity of some function symbol $f$ \cite{TRS}.
\section{Equational Unification}
In the following let $E$ be a set of identities of the form $\left\lbrace  e_1\approx f_1,\dots,e_n\approx f_n \right\rbrace$. Furthermore let $\mathcal{S}ig(E)$ denote the set of all function symbols occurring in $E$. Let $\Sigma$ be a finite set of function symbols which is a superset of $\mathcal{S}ig(E)$.
\begin{definition}
	An \textbf{\mBold-unification problem} over $\Sigma$ is a finite set $S$ of the form $S=\left\lbrace s_1\approxq_{E} t_1,\dots,s_n\approxq_{E} t_n\right\rbrace $ with $s_1,\dots,s_n,t_1,\dots,t_n \in\TermSet$, $V$ being a countable set of variables.
		
	A substitution $\sigma$ is an \textbf{\mBold-unifier} of $S$ iff $ \sigma(s_i)\approx_E \sigma(t_i)$ for all $1\leq i \leq n$.
	The set of all $E$-unifiers of $S$ is denoted by $\mathcal{U}_E(S)$. The problem $S$ is \textbf{\mBold-unifiable} iff $\mathcal{U}_E(S)\neq \emptyset$.
\end{definition}
If an $E$-unification problem $S$ contains only one equation $s\approxq_E t$ we often omit the brackets and write $S=s\approxq_E t$. We can now classify unification problems according to the symbols occurring in them.
\begin{definition}
	Let $S$ be an $E$-unification problem over $\Sigma$.
	\begin{itemize}
		\item $S$ is an \textbf{elementary} $E$-unification problem iff $\mathcal{S}ig(E)=\Sigma$.
		\item $S$ is an $E$-unification problem \textbf{with constants} iff $\Sigma-\mathcal{S}ig(E)\subseteq\Sigma^{(0)}$ and $\mathcal{S}ig(E)\subset\Sigma$.
		\item $S$ is an \textbf{general} $E$-unification problem iff $\Sigma-\mathcal{S}ig(E)$ contains an at least unary function symbol.
	\end{itemize}
\end{definition}
One \emph{most general unifier} does not always suffice to represent $\mathcal{U}_E(S)$. In this case we need an \emph{E-minimal E-complete set of E-unifiers} but to define this set we first need an order on substitutions.
\begin{definition}
	Let $X$ be a set of variables. A substitution $\sigma$ is \textbf{more general} modulo $\approx_E$ than a substitution $\sigma'$ on $X$ iff there is a substitution $\delta$ such that $\delta(\sigma(x))\approx_E\sigma'(x)$ for all $x \in X$. We denote this by $\sigma\moreGeneral\sigma'$.
\end{definition}
The order $\moreGeneral$ is a quasi order since it obviously is reflexive and transitive. To see why we only demand equality modulo $\approx_E$ on $X$ and not on all variables like we did in syntactic unification we first need to define \emph{E-minimal E-complete sets}.
Let us denote the variables occurring in an $E$-unification problem $S$ by $\mathcal{V}ar(S)$.
\begin{definition}
	Let $S$ be an $E$-unification problem over $\Sigma$ and let $X:=\mathcal{V}ar(S)$. An \textbf{\mBold-complete} set for $S$ is a set of substitutions $\mathcal{C}$ that satisfies the following properties:
	\begin{itemize}
		\item each $\sigma \in \mathcal{C}$ is an $E$-unifier of $S$
		\item for all $\theta \in\mathcal{U}_E(S)$ there exists a $\sigma \in \mathcal{C}$ such that $\sigma\moreGeneral\theta$
	\end{itemize}
	An \textbf{\mBold-minimal \mBold-complete} set is an $E$-complete set  $\mathcal{M}$ that satisfies the additional property
	\begin{itemize}
		\item for all $\sigma,\sigma'\in\mathcal{M},\ \sigma\moreGeneral\sigma'$ implies $\sigma=\sigma'$.
	\end{itemize}
	The substitution $\sigma$ is a \textbf{most general \mBold-unifier} (mgu) of $S$ iff $\left\lbrace \sigma\right\rbrace$ is an $E$-minimal $E$-complete set of $S$.
\end{definition}
Now to understand why the restriction to $X$ makes sense note that by the restriction to variables in $X$ more substitutions are comparable with respect to $\moreGeneral$ since we do not demand equality modulo $\approx_E$ on all variables. It is easy to see that if $X=\mathcal{V}ar(S)$, $\sigma$ is an $E$-unifier of $S$ and $\sigma\moreGeneral\sigma'$, then $\sigma'$ is also an $E$-unifier of $S$. This only shows that restricting to $X$ does not do any damage. The reason it is useful is that there are $E$-unification problems $S$ for which any $E$-minimal $E$-complete set of $E$-unifiers has to contain variables not occurring in $S$. For a proof that such $E$ and $S$ really do exist look at .
%TODO reference
 
Let us consider a small example to see the problem that occurs when we have new variables in $E$-minimal $E$-complete sets. Pretend that there exists an $E$-unification problem $S$ with an $E$-minimal $E$-complete set $\mathcal{M}$ such that $\mathcal{V}ar(S)=\left\lbrace x\right\rbrace$, $\sigma:=\left\lbrace x\mapsto f(y)\right\rbrace\in\mathcal{M}$ and $ a\not\approx_E x$. 
Clearly $\sigma':=\left\lbrace x\mapsto f(a)\right\rbrace$ is also an $E$-unifier of $S$ but $\sigma$ and $\sigma'$ are incomparable with respect to $\lesssim^{\left\lbrace x,y\right\rbrace }_E$. The substitution $\delta:=\left\lbrace y\mapsto a\right\rbrace $ does not work here since $\delta(\sigma(y))=a \not\approx_E y=\sigma'(y)$ which means there has to be another unifier $\sigma''$ in $\mathcal{M}$ with $\sigma''\lesssim^{\left\lbrace x,y\right\rbrace }_E\sigma$. But if we restrict $X$ to $\left\lbrace x\right\rbrace $ we only need that $\delta(\sigma(x))=f(a)=\sigma'(x)$, so $\sigma\lesssim^{\left\lbrace x\right\rbrace }_E\sigma'$ holds. We see that $E$-minimal $E$-complete sets can become unnecessary large if we consider all variables.

Now let us consider an example in which an $E$-minimal $E$-complete set contains infinitely many elements. Let $A:=\left\lbrace x+(y+z)\approx (x+y)+z\right\rbrace $ be a set of identities and $S:=\left\lbrace x+a\approxq_A a+x\right\rbrace$ an $A$-unification problem over $\Sigma:=\left\lbrace +,a\right\rbrace$. For $n>0$, we define substitutions $\sigma_n$ inductively as follows:
\begin{align*}
	\sigma_1     & :=\left\lbrace x\mapsto a\right\rbrace             \\
	\sigma_{n+1} & :=\left\lbrace x\mapsto a+\sigma_n(x)\right\rbrace 
\end{align*}
Since $A$ axiomatizes associativity we can omit the brackets and give an explicit definition of $\sigma_n$.
\begin{align*}
	\sigma_n:=\lbrace x\mapsto\underbrace{a+\dots+a}_{n\times a} \rbrace 
\end{align*}
Now it is easy to see that all $\sigma_n$ are $A$-unifiers of $S$.
Let us consider an arbitrary $A$-unifier $\theta$ of $S$. The substitution $\theta$ has the form $\theta(x):=x_1+\dots+x_n$ where the $x_i's$ are either a constant (e.g. $a$ or $b$) or a variable.
Since $\theta$ is an $A$-unifier of $S$ we know that:
\begin{align*}
	  &                     & \theta(x)+a                                 & \approx_A a+\theta(x)                      \\
	  & \implies            & x_1+x_2+\dots+x_n+a                         & \approx_A a+x_1+\dots+x_{n-1}+x_n          \\
	  & \implies x_1=x_n=a  & a\hphantom{_1}+x_2+\dots+ a \hphantom{_n}+a & \approx_A a+a\hphantom{_n}+\dots+x_{n-1}+a \\
	  & \hspace{10pt}\vdots &                                             & \vdots                                     
\end{align*}
Now it follows that $x_2$ and $x_{n-1}$ have to be $a$. From that we get $x_3=a$ and $x_{n-2}=a$ and so on until $x_i=a$ for every $1\leq i\leq n$.
%really \approx_A and not = since the brakets can be different 
So $\theta(x)\approx_A\sigma_n(x)$ which implies $\sigma\lesssim^{\left\lbrace x\right\rbrace }_A\theta$.
Since we picked $\theta$ arbitrarily this yields $A$-completeness of the set $\mathcal{M}:=\bigcup_{n>0}\left\lbrace  \sigma_n\right\rbrace $.
All $\sigma_n$ are distinct and map x to ground terms. Hence they are pairwise incomparable with respect to $\lesssim^{\left\lbrace x\right\rbrace }_A$. This yields $A$-minimality of $\mathcal{M}$.
We see that $E$-minimal $E$-complete sets do not need to have finite cardinality.

We denote the equivalence class induced by $\moreGeneral$ with $\eqClass$.
\begin{center}
	$\sigma\eqClass\sigma'$ iff $\sigma\moreGeneral\sigma'$ and $\sigma'\moreGeneral\sigma$
\end{center}
\begin{lemma}
	Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $E$-minimal $E$-complete sets of $S$. Then there exists a bijective mapping $B:\mathcal{M}_1\to\mathcal{M}_2$ such that $\sigma_1\eqClass B(\sigma_1)$ for all $\sigma_1\in\mathcal{M}_1$.
\end{lemma}
\begin{proof}
	We define a mapping $B:\mathcal{M}_1\to\mathcal{M}_2$ such that $B(\sigma_1)\moreGeneral\sigma_1$ for all $\sigma_1\in\mathcal{M}_1$. This is possible since $\mathcal{M}_1\subseteq\mathcal{U}_E(S)$ and $E$-completeness of $\mathcal{M}_2$ yields that for every $\sigma_1\in\mathcal{M}_1$ there exists a $\sigma_2\in\mathcal{M}_2$ such that $\sigma_2\moreGeneral\sigma_1$. We define $B':\mathcal{M}_2\to\mathcal{M}_1$ in a similar way.
	\begin{center}
		\begin{tikzpicture}
			\newcommand{\vLength}{1.5}
			\tikzset{vertex/.style = {circle,draw,fill=black,minimum size=4pt,inner sep=0pt}}
			\tikzstyle{edge} = [->,> = latex',thin]
			\tikzstyle{edgeThick} = [->,> = latex', ultra thick]
			%M_1
			\node[vertex] (00) at (0,\vLength) [label=left:$\mathcal{M}_1:$] {};
			\node[vertex] (01) at (1,\vLength) {};
			\node[vertex] (02) at (2,\vLength) [label=above:\small{$\sigma_1$}] {};
			\node[vertex] (03) at (3,\vLength) {};
			\node[vertex] (04) at (4,\vLength) {};
			%M_2
			\node[vertex] (10) at (0,0) [label=left:$\mathcal{M}_2:$] {};
			\node[vertex] (11) at (1,0) {};
			\node[vertex] (12) at (2,0) {};
			\node[vertex] (13) at (3,0) [label=right:\hspace{-4pt}\small{$B(\sigma_1)$}] {};
			\node[vertex] (14) at (4,0) {};
			%M_1 bottom
			\node[vertex] (20) at (0,-\vLength)[label=left:$\mathcal{M}_1:$] {};
			\node[vertex] (21) at (1,-\vLength) {};
			\node[vertex] (22) at (2,-\vLength) [label=below:\small{$B'(B(\sigma_1))$}] {};
			\node[vertex] (23) at (3,-\vLength) {};
			\node[vertex] (24) at (4,-\vLength) {};
			%mapping B
			\draw[edge] (00) to (11);
			\draw[edge] (01) to (10);
			\draw[edgeThick] (02) to (13);
			\draw[edge] (03) to (14);
			\draw[edge] (04) to (12);
			%mapping B'
			\draw[edge] (11) to (20);
			\draw[edge] (10) to (21);
			\draw[edgeThick] (13) to (22);
			\draw[edge] (14) to (23);
			\draw[edge] (12) to (24);
							
			\node[rotate=90] (B) at (4.5,0.5*\vLength) {$\moreGeneral$};
			\node[rotate=90] (B') at (4.5,-0.5*\vLength) {$\moreGeneral$};
		\end{tikzpicture}
	\end{center}
	Since by definition $B'(B(\sigma_1))\moreGeneral B(\sigma_1)\moreGeneral\sigma_1$ $E$-minimality of $\mathcal{M}_1$ implies that $B'(B(\sigma_1))=\sigma_1$ for all $\sigma_1\in\mathcal{M}_1$. Symmetrically, $B(B'(\sigma_2))=\sigma_2$ for all $\sigma_2\in\mathcal{M}_2$. It follows that $B$ is a bijection and $B'=B^{-1}$.
	\begin{center}
		\begin{tikzpicture}
			\newcommand{\vLength}{1.5}
			\tikzset{vertex/.style = {circle,draw,fill=black,minimum size=4pt,inner sep=0pt}}
			\tikzstyle{edge} = [<->,> = latex',thin]
			\tikzstyle{edgeThick} = [<->,> = latex', ultra thick]
			%M_1
			\node[vertex] (00) at (0,\vLength) [label=left:$\mathcal{M}_1:$] {};
			\node[vertex] (01) at (1,\vLength) {};
			\node[vertex] (02) at (2,\vLength) [label=above:\tiny{$\sigma_1=B'(B(\sigma_1))$}] {};
			\node[vertex] (03) at (3,\vLength) {};
			\node[vertex] (04) at (4,\vLength) {};
			%M_2
			\node[vertex] (10) at (0,0) [label=left:$\mathcal{M}_2:$] {};
			\node[vertex] (11) at (1,0) {};
			\node[vertex] (12) at (2,0) {};
			\node[vertex] (13) at (3,0) [label=below:\small{$B(\sigma_1)$}] {};
			\node[vertex] (14) at (4,0) {};
			%mapping B
			\draw[edge] (00) to (11);
			\draw[edge] (01) to (10);
			\draw[edgeThick] (02) to (13);
			\draw[edge] (03) to (14);
			\draw[edge] (04) to (12);
							
			\node[rotate=90] (B) at (4.5,0.5*\vLength) {$\eqClass$};
		\end{tikzpicture}
	\end{center}
\end{proof}
The most interesting consequence of this lemma is that $E$-minimal $E$-complete sets of the same $S$ always have the same cardinality. This allows us to classify equational theories $\approx_E$ by the existence and possible cardinalities of $E$-minimal $E$-complete sets of $E$-unification problems.
\begin{definition}
	The equational theory $\approx_E$ is of \textbf{unification type}
	\begin{description}
		\item[\textbf{unitary}] iff for all $E$-unification problems $S$ there exists an $E$-minimal $E$-complete set of cardinality $\leq 1$.
		%if S has no solution M=\emptyset
		\item[\textbf{finitary}] iff for all $E$-unification problems $S$ there exists an $E$-minimal $E$-complete set with finite cardinality.
		\item[\textbf{infinitary}] iff for all $E$-unification problems $S$ there exists an $E$-minimal $E$-complete set, and there exists an $E$-unification problem for which this set is infinite.
		\item[\textbf{zero}] iff there exists an $E$-unification problem that does not have an $E$-minimal $E$-complete set.
	\end{description}
\end{definition}
Note that if the $E$-unification problem $S$ has no $E$-unifiers then the empty set is an $E$-minimal $E$-complete set of $S$. The empty set is $E$-complete because there are no $\sigma\in\emptyset$ and $\mathcal{U}_E$ is empty. $E$-minimality holds trivially. This is the reason we allow the cardinalities 0 and 1 in the \emph{unitary} case.
An example for a \emph{finitary} theory that is not \emph{unitary} is $\mathcal{C}:=\left\lbrace f(x,y)\approx f(y,x)\right\rbrace$ which axiomatizes commutativity.
With $\mathcal{A}:=\left\lbrace x+(y+z)\approx (x+y)+z\right\rbrace$ the theory that axiomatizes associativity we have already seen an example for an \emph{infinitary} equational theory.
%TODO example for type zero

In the definition of the \emph{unification types} we allowed for arbitrary $E$-unification problems but if we distinguish between elementary $E$-unification problems, $E$-unification problems with constants and general $E$-unification problems we might end up with different \emph{unification\ types}.